Location and Scale-Invariant Power Transformations for Transforming Data to

### 2024-09-11 manuscript/manuscript.Rmd
Updated data and code availability

Location- and scale-invariant power transformations are implemented in the `power.transform` package for R, and is available from [https://github.com/oncoray/power.transform] and the CRAN repository [INSERT LINK HERE]. The manuscript was created using R Markdown and is also available from the power.transform GitHub repository. Data and results for the machine learning experiment are separately available from Zenodo [INSERT LINK HERE].

>>>>

Location- and scale-invariant power transformations were implemented in the `power.transform` package for R, which is available from [https://github.com/oncoray/power.transform] and the CRAN repository [INSERT LINK HERE]. The manuscript was created using R Markdown and is likewise available from the `power.transform` GitHub repository. Data and results for the machine learning experiment are separately available from Zenodo [https://doi.org/10.5281/zenodo.13736671].
